My title

### 2024-02-14 outputs/paper/paper.qmd
Added all files related to staff-student ratios

library(tidyverse) # a collection of data-related packages
library(knitr) # for kable
library(kableExtra)
library(here)
library(ggbeeswarm)
library(ggplot2)

#reading cleaned data

state_score = read_csv(file = here("outputs/data/cleaned_state_scoredata.csv"),       
  show_col_types = FALSE
)

head(state_score)

rhode = read_csv(
  file = here("outputs/data/cleaned_learningmodel/rhode.csv"),       
  show_col_types = FALSE
)

@@

@@

## Data Source and Collection

The data utilized in this study is obtained from the compilation of district-level schooling models and state standardized assessment data, originally featured in the paper "Pandemic Schooling Mode and Student Test Scores: Evidence from US School Districts" [@citepaper] published in the American Economic Review: Insights in June 2023. [@citewebsite]. The primary dataset encompasses schooling mode data from the 2020–2021 academic year across 11 U.S. states, integrating various educational approaches during the pandemic, including in-person, hybrid, and virtual learning environments. These datasets were sourced from COVID-19 School Data Hub [@citedata], district-level state standardized assessment data from spring
2016–2019 and 2021, and additional data demographic statistics from the National Center for Education Statistics (NCES) to establish a comprehensive analytical framework. We also used additional year 2020 household data by Household Pulse Survey [@citehousehold] from  U.S. Census Bureau spanning weeks 1 to 12.

Our analyses incorporate three categories of data: district-level schooling modes, state standardized assessment results from the academic years 2016–2019 and 2021, and auxiliary  that encompass district demographics and county-level variables. The following subsections detail the sources, collection methodologies, and data cleaning procedures undertaken to ensure the accuracy and reliability of the datasets for our analysis.

**State Score Data**: This dataset encompasses state-level academic performance statistics from 2016 to 2020. Variables include the proportion of in-person, virtual, and hybrid learning, participation rates, standardized test pass rates, COVID-19 case rates per 100,000 in school zip codes, peak monthly cases, total enrollment figures, and political voting shares by district.

**Learning Model Data**: This dataset details the learning models adopted by school districts in Colorado, Connecticut, Ohio, Virginia, West Virginia, Wyoming, Mississippi, Rhode Island, Minnesota, Massachusetts, and Wisconsin. Each state's data outlines the specific learning model (in-person, virtual, hybrid) employed over time, enrollment figures, and staffing counts.

## Data Cleaning and Processing
We used R [@citeR] for data cleaning and processing, utilizing packages like tidyverse [@tidyverse] for data manipulation and janitor [@citejan] for cleaning column names. The cleaning process involved standardizing learning model categories, selecting columns of interest, and simplifying data for analysis. We integrated data from different states, and made sure that variations in reporting and measurement were addressed while combining them into one. For instance, some states categorized their schooling mode as "In-person," while others used "In-Person." To ensure they are equivalent, we standardized these terms. We also conducted a check for missing data values, and imputed or excluded them as appropriate based on the context. The variables were also renamed for clarity and consistency across different states' datasets.  A sample of cleaned state score data can be seen in [@tbl_cleaned_data].

```{r tbl_cleaned_data}
#| message: false
#| echo: false
#| warning: false
#| tbl-cap: Sample of Cleaned State Score Data
#| label: tbl_cleaned_data

library(kableExtra)
library(knitr)

options(kableExtra.latex.max.width=1)
head(state_score, 6) |>
  kable(
        col.names = c("State", "Year", "Share In-person", "Share Virtual", "Share Hybrid", "Participation", "Pass Rate", "Covid cases rate per 100k", "Total Enrollment"),
    booktabs = TRUE,
    longtable = FALSE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down"), font_size = 6)
```

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false
#| warning: false

@@

state_score <- na.omit(state_score)

@@

ggplot(state_score, aes(x = case_rate_per100k_zip, y = pass)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(x = "COVID-19 Case Rate per 100k", y = "Passing Rate", 
       title = "Correlation between Passing Rate and COVID-19 Case Rate per 100k") +
  theme_minimal() +
  xlim(0, 350)

ggplot(state_score, aes(x = case_rate_per100k_zip, y = pass)) +
  geom_point() +  # Add points
  geom_smooth(method = "lm", se = FALSE) +  # Add a linear regression line without standard error bands
  labs(x = "COVID-19 Case Rate per 100k", y = "Passing Rate", 
       title = "Correlation between Passing Rate and COVID-19 Case Rate per 100k") +
  theme_minimal()
# Print the results of the correlation test

# Create a box plot
state_score <- state_score %>% 
  filter(!is.na(case_rate_per100k_zip) & !is.nan(case_rate_per100k_zip))

state_score$category <- cut(state_score$case_rate_per100k_zip, 
                            breaks = quantile(state_score$case_rate_per100k_zip, 
                                              probs = 0:3/3, na.rm = TRUE), 
                            include.lowest = TRUE, 
                            labels = c("Low", "Medium", "High"))

# Create a box plot with colors
ggplot(state_score, aes(x = category, y = pass, fill = category)) +
  geom_boxplot() +
  labs(title = "Box Plot of Passing Rates by COVID-19 Case Rate Categories", 
       x = "COVID-19 Case Rate Category", 
       y = "Passing Rate") +
  theme_minimal() +
  scale_fill_brewer(palette = "Pastel1")

ggplot(state_score, aes(x = pass)) +
  geom_density(fill = "blue", alpha = 0.5) +
  labs(title = "Density Plot of Passing Rates", x = "Passing Rate", y = "Density") +
  theme_minimal()

```
## Data Modifications

In this study, we developed a unique dataset by carefully selecting and combining data from the Household Pulse Survey, available from the U.S. Census Bureau for weeks 1 to 12. This process involved choosing key variables that were crucial for our research. We aimed to analyze the connection between economic changes, particularly the loss of employment income, and their impact on educational outcomes, focusing specifically on school passing rates. This helped us to understand the relationship between these economic factors and educational performance. To ensure consistency, we standardized terminologies and measurements, and aligned variables such as timeframes and demographic categories across the datasets. For example, we combined the state score data with the weekly household data, aligned variables relevant to our study. The merged data file was thereafter saved as a CSV file to study the trends later on.

@@

data_2019 <- state_score %>%
  filter(year == 2019) %>%
  group_by(state) %>%
  summarise(
    avg_share_inperson = mean(share_inperson, na.rm = TRUE)*100,
    avg_share_virtual = mean(share_virtual, na.rm = TRUE)*100,
    avg_share_hybrid = mean(share_hybrid, na.rm = TRUE)*100,
    avg_participation = mean(participation, na.rm = TRUE),
    avg_pass_rate = mean(pass, na.rm = TRUE)*100
  )

data_2021 <- state_score %>%
  filter(year == 2021) %>%
  group_by(state) %>%
  summarise(
    avg_share_inperson = mean(share_inperson, na.rm = TRUE)*100,
    avg_share_virtual = mean(share_virtual, na.rm = TRUE)*100,
    avg_share_hybrid = mean(share_hybrid, na.rm = TRUE)*100,
    avg_participation = mean(participation, na.rm = TRUE),
    avg_pass_rate = mean(pass, na.rm = TRUE)*100
  )

options(kableExtra.latex.max.width = 1)
data_2019 %>% 
  kable(format = "markdown", 
        col.names = c("State", "Avg. Share In-person", "Avg. Share Virtual", "Avg. Share Hybrid", "Avg. Participation", "Avg. Pass Rate"),
        booktabs = TRUE,
        longtable = FALSE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down"), font_size = 9)

options(kableExtra.latex.max.width = 1)
data_2021 %>% 
  kable(format = "markdown", 
        col.names = c("State", "Avg. Share In-person", "Avg. Share Virtual", "Avg. Share Hybrid", "Avg. Participation", "Avg. Pass Rate"),
        booktabs = TRUE,
        longtable = FALSE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down"), font_size = 9)

inperson_data <- state_score %>%
  select(state, share_inperson)

# Step 2: Plot the data
ggplot(inperson_data, aes(x = state, y = share_inperson)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Box Plot of In-Person Learning Model Share Across States",
       x = "State", y = "Share of In-Person Learning") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

virtual_data <- state_score %>%
  select(state, share_virtual)

# Plot for virtual learning model
ggplot(virtual_data, aes(x = state, y = share_virtual)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Box Plot of Virtual Learning Model Share Across States",
       x = "State", y = "Share of Virtual Learning") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Prepare data for hybrid learning model
hybrid_data <- state_score %>%
  select(state, share_hybrid)

# Plot for hybrid learning model
ggplot(hybrid_data, aes(x = state, y = share_hybrid)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Box Plot of Hybrid Learning Model Share Across States",
       x = "State", y = "Share of Hybrid Learning") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(state_score, aes(x = share_virtual, y = pass)) +
  geom_point() +  # Add points to the plot
  geom_smooth(method = "lm", se = FALSE) +  # Add a linear trend line without the shaded confidence interval
  theme_minimal() +
  labs(title = "Scatter Plot of Virtual Learning Share vs. Passing Rate",
       x = "Share of Virtual Learning", y = "Passing Rate") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

state_with_highest_virtual <- state_score %>%
  group_by(state) %>%
  summarize(average_virtual = mean(share_virtual, na.rm = TRUE)) %>%
  arrange(desc(average_virtual)) %>%
  slice(1) %>%
  pull(state)

# Filter the data for the state with the highest virtual learning
state_passing_data <- state_score %>%
  filter(state == state_with_highest_virtual)

# Plot the passing rates against the case rate per 100k for the state with the highest virtual learning
ggplot(state_passing_data, aes(x = case_rate_per100k_zip, y = pass)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +  # Add a linear trend line
  theme_minimal() +
  labs(title = paste("Passing Rate vs. Case Rate per 100k in", state_with_highest_virtual),
       x = "Case Rate per 100k", y = "Passing Rate") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

state_with_highest_cases <- state_score %>%
  group_by(state) %>%
  summarize(average_cases = mean(case_rate_per100k_zip, na.rm = TRUE)) %>%
  arrange(desc(average_cases)) %>%
  slice(1) %>%
  pull(state)

# Filter the data for the state with the highest case rate per 100k
state_passing_data <- state_score %>%
  filter(state == state_with_highest_cases)

# Plot the passing rates for the state with the highest case rate per 100k
ggplot(state_passing_data, aes(x = as.factor(year), y = pass, group = state, color = state)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = paste("Passing Rate in", state_with_highest_cases, "with the Highest COVID-19 Case Rate"),
       x = "Year", y = "Passing Rate") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Find the state with the lowest case rate per 100k
state_with_lowest_cases <- state_score %>%
  group_by(state) %>%
  summarize(average_cases = mean(case_rate_per100k_zip, na.rm = TRUE)) %>%
  arrange(average_cases) %>%
  slice(1) %>%
  pull(state)

# Filter the data for the state with the lowest case rate per 100k
state_passing_data_lowest <- state_score %>%
  filter(state == state_with_lowest_cases)

# Plot the passing rates for the state with the lowest case rate per 100k
ggplot(state_passing_data_lowest, aes(x = as.factor(year), y = pass, group = state, color = state)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(title = paste("Passing Rate in", state_with_lowest_cases, "with the Lowest COVID-19 Case Rate"),
       x = "Year", y = "Passing Rate") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

We can use maths by including latex between dollar signs,  instance $\theta$.

>>>>

library(tidyverse) # a collection of data-related packages
library(knitr) # for kable
library(kableExtra)
library(here)
library(ggbeeswarm)

#reading cleaned data
rhode = read_csv(
  file = here("outputs/data/cleaned_learningmodel/rhode.csv"),       
  show_col_types = FALSE
)

@@

scores = read_csv(
  file = here("outputs/data/all_scoredata.csv"),       
  show_col_types = FALSE
)
scores_2019 = read_csv(
  file = here("outputs/data/score_ohio.csv"),       
  show_col_types = FALSE
)
merged_data = read_csv(file = here("outputs/data/merged_data_by_state.csv"), show_col_types = FALSE)

```{r}
#| label: Vanshika-graphs
#| fig-cap: lets see
#| echo: false
# Plotting passing rates for each state
ggplot(scores, aes(x = state, y = pass, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "Passing Rates Across Different States",
       x = "State",
       y = "Passing Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
# graph of all the passing rate all the different states

# Calculate the difference between passing rates
pass_diff <- scores$pass - mean(scores$pass)

# Plotting
ggplot(scores, aes(x = state, y = pass_diff, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "Difference in Passing Rates Between States",
       x = "State",
       y = "Difference in Passing Rates") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# The lowest passing rates were Rhode Island

# graph for rode island and its unemployemnt during covid
# Plotting passing rates for each state
rhode_island_data <- subset(scores, state == "RI")
ggplot(scores, aes(x = state , y = unemployment, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "unemployment Across Different States",
       x = "State",
       y = "Unemployemtn Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
# graph of all the passing rate all the different states

ggplot(scores, aes(x = state , y = cts_pass_advanced, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "advanced Passing Rates Across Different States",
       x = "State",
       y = "Passing Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(scores, aes(x = state , y = cts_pass_proficient, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "profient Passing Rates Across Different States",
       x = "State",
       y = "Passing Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(scores, aes(x = state , y = cts_pass_approaching, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "approaching Passing Rates Across Different States",
       x = "State",
       y = "Passing Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(scores, aes(x = state , y = cts_pass_partially, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "Partially Passing Rates Across Different States",
       x = "State",
       y = "Passing Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(scores, aes(x = state , y = cts_pass_below, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "below Passing Rates Across Different States",
       x = "State",
       y = "Passing Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# DATA WITH ONLY 2019
ggplot(scores_2019, aes(x = state, y = pass, fill = state)) +
  geom_bar(stat = "identity") +
  labs(title = "Passing Rates In 2019",
       x = "State",
       y = "Passing Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```{r}
#| label: Vanshika-RI
#| fig-cap: lets see
#| echo: false
library(reshape2)
# Select relevant columns for correlation analysis
correlation_data <- scores[, c("pass", "participation", "share_black", "share_white", "share_hisp", "share_lunch", "unemployment")]

# Calculate correlation matrix
correlation_matrix <- cor(correlation_data, use="complete.obs")

# Convert the correlation matrix to a data frame
correlation_df <- melt(correlation_matrix)

# Plotting the correlation heatmap
correlation_heatmap <- ggplot(correlation_df, aes(Var1, Var2, fill=value)) +
  geom_tile(color="white") +
  scale_fill_gradient2(low="blue", mid="white", high="red", midpoint=0, limit=c(-1,1), space="Lab", name="Correlation") +
  theme_minimal() +
  labs(title = "Correlation Analysis: Heatmap of Correlation Coefficients",
       x = "Variables",
       y = "Variables") +
   theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# Display the heatmap
correlation_heatmap

# Select relevant columns for correlation analysis
correlation_data <- scores[, c("share_inperson", "share_virtual", "share_hybrid", "pass", "participation", "share_black", "share_white", "share_hisp", "unemployment")]

# Calculate correlation matrix
correlation_matrix <- cor(correlation_data, use="complete.obs")

# Convert the correlation matrix to a data frame
correlation_df <- melt(correlation_matrix)

# Plotting the correlation heatmap with vertical x-axis labels
correlation_heatmap <- ggplot(correlation_df, aes(Var1, Var2, fill=value)) +
  geom_tile(color="white") +
  scale_fill_gradient2(low="blue", mid="white", high="red", midpoint=0, limit=c(-1,1), space="Lab", name="Correlation") +
  theme_minimal() +
  labs(title = "Correlation Analysis: Heatmap of Correlation Coefficients",
       x = "Variables",
       y = "Variables") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

# Display the heatmap
correlation_heatmap

# Select relevant columns for correlation analysis
correlation_data <- scores %>%
  select(state, participation, share_inperson)

# Calculate correlation matrix by grouping data by state and then calculating correlations
correlation_matrix <- correlation_data %>%
  group_by(state) %>%
  summarise(correlation = cor(participation, share_inperson))

# Plotting the correlation graph
correlation_graph <- ggplot(correlation_matrix, aes(x = state, y = correlation)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
  labs(title = "Correlation between Participation Rate and Share In Person by State",
       x = "State",
       y = "Correlation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Display the correlation graph
correlation_graph

# coorelation between virtual and participation
# Select relevant columns for correlation analysis
correlation_data <- scores %>%
  select(state, participation, share_virtual)

# Calculate correlation matrix by grouping data by state and then calculating correlations
correlation_matrix <- correlation_data %>%
  group_by(state) %>%
  summarise(correlation = cor(participation, share_virtual))

# Plotting the correlation graph
correlation_graph <- ggplot(correlation_matrix, aes(x = state, y = correlation)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.5) +
  labs(title = "Correlation between Participation Rate and Share virtual by State",
       x = "State",
       y = "Correlation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Display the correlation graph
correlation_graph

# corelation between pass and unemployemnt 
# Select relevant columns for correlation analysis
correlation_data <- scores %>%
  select(state, unemployment, pass)

# Calculate correlation matrix by grouping data by state and then calculating correlations
correlation_matrix <- correlation_data %>%
  group_by(state) %>%
  summarise(correlation = cor(unemployment, pass))

# Plotting the correlation graph
correlation_graph <- ggplot(correlation_matrix, aes(x = state, y = correlation)) +
  geom_bar(stat = "identity", fill = "purple", width = 0.5) +
  labs(title = "Correlation between Unemployement Rate and passing rate by State",
       x = "State",
       y = "Correlation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Display the correlation graph
correlation_graph
```

```{r}
#| label: Random Graphs
#| fig-cap: lets see
#| echo: false

library(ggplot2)

# Passing rate trends over different years and subjects
passing_rate_trends <- ggplot(scores, aes(x = year, y = pass, color = subject)) +
  geom_line() +
  labs(title = "Passing Rate Trends Over Different Years and Subjects",
       x = "Year",
       y = "Passing Rate",
       color = "Subject") +
  theme_minimal()

# Variations between different districts or states
passing_rate_variations <- ggplot(scores, aes(x = state, y = pass, fill = state)) +
  geom_boxplot() +
  labs(title = "Variations in Passing Rates Between Different States",
       x = "State",
       y = "Passing Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Display the graphs
passing_rate_trends
passing_rate_variations

# Investigating participation rates across districts or states
participation_rates <- ggplot(scores, aes(x = state, y = participation, fill = state)) +
  geom_boxplot() +
  labs(title = "Participation Rates Across Different States",
       x = "State",
       y = "Participation Rate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Display the graph
participation_rates

# Relationship between demographic factors and passing rates
demographic_analysis <- ggplot(scores, aes(x = share_black, y = pass)) +
  geom_point() +
  labs(title = "Relationship Between Percentage of Black Students and Passing Rate",
       x = "Percentage of Black Students",
       y = "Passing Rate") +
  theme_minimal()

# Display the graph
demographic_analysis

# Comparing passing rates between different subjects
subject_comparison <- ggplot(scores, aes(x = subject, y = pass, fill = subject)) +
  geom_boxplot() +
  labs(title = "Passing Rates Comparison Between Different Subjects",
       x = "Subject",
       y = "Passing Rate") +
  theme_minimal()

# Display the graph
subject_comparison

@@

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

@@

all_states$time_period_start <- as.Date(all_states$time_period_start, format = "%Y-%m-%d")
all_states$learning_model <- as.factor(all_states$learning_model)

library(ggplot2)

# ggplot(all_states, aes(x = time_period_start, y = learning_model, color = state)) +
#   geom_line() +
#   labs(title = "Comparison of Learning Models in US States Over Time",
#        x = "Time Period Start", y = "Learning Model") +
#   theme_minimal() +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))

# ggplot(all_states, aes(x = time_period_start, y = learning_model, group = state, color = state)) +
#   geom_line() +
#   scale_x_date(date_breaks = "1 month", date_labels = "%b %Y") +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1)) # Rotate x-axis labels if needed
#

#tthis graph is correct, but causing scale bias, since data is large for some states like Minnesota has 21000 rows, but low for few states like Colorado which only has 1600 rows,
# learning_model_summary <- all_states %>%
#   count(state, learning_model) %>%
#   ungroup()
# 
# # Plotting with a bar graph
# ggplot(learning_model_summary, aes(x = state, y = n, fill = learning_model)) + 
#   geom_bar(stat = "identity", position = "dodge") +
#   theme_minimal() +
#   labs(x = "State", y = "Frequency of Learning Model", fill = "Learning Model", 
#        title = "Comparison of Learning Models in US States") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

```{r}
#| label: Navya
#| fig-cap: Relationship between teacher and pass rates
#| echo: false
#| warning: false
#| message: false
# Define colors for each state
state_colors <- rainbow(length(unique(merged_data$state)))

# Create a scatter plot with colored points
plot(merged_data$average_students_per_teacher, merged_data$average_pass, 
     xlab = "Average Students per Teacher", ylab = "Average Pass Rates",
     main = "Relationship Between Average Students per Teacher and Average Pass Rates",
     col = state_colors[as.factor(merged_data$state)], pch = 19)

# Add labels for each point
text(merged_data$average_students_per_teacher, merged_data$average_pass, labels = merged_data$state, pos = 3, cex = 0.8)

# Fit a linear regression model
lm_model <- lm(average_pass ~ average_students_per_teacher, data = merged_data)

# Add a trend line
abline(lm_model, col = "red")

# Add a legend
legend("bottomright", legend = unique(merged_data$state), col = state_colors, pch = 19, cex = 0.8, title = "State")

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

@@

@@

We can use maths by including latex between dollar signs, for instance $\theta$.
